A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-06-24 nips2015.tex
refactor .tex

\title{
  %\hrule\hrule\bigskip\bigskip
  A simple and efficient algorithm for computing approximate
  Nash equilibria in two-person zero-sum games with imcomplete
  information}
\author{Elvis DOHMATOB
\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
\\\texttt{firstname.lastname@inria.fr}
}

@@

\subsection{Our contribution}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
  \epsilon$)-equilibria (in a sense to be made clear later in
  Definition \ref{thm:cool_notion}) for
  sequential two-person zero-sum games with imcomplete information and
  perfect recall.

@@

\section{The proposed algorithm}
\label{sec:algo}
\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.
\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ is the set-valued function
\begin{eqnarray}
\partial_\epsilon f: \mathbb{R}^n \rightarrow
2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}
\end{definition}

\subsection{Algorithm and convergence rate}
We now derive the algorithm derive the algorithm which is the main object of
this manuscript.

>>>>

\title{
  %\hrule\hrule\bigskip\bigskip
  A simple and efficient algorithm for computing approximate
  Nash equilibria in two-person zero-sum sequential games with imcomplete
  information}
\author{Elvis DOHMATOB
\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
\\\texttt{firstname.lastname@inria.fr}
}

@@

Let us introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.

\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ is the set-valued function
\begin{eqnarray}
\partial_\epsilon f: \mathbb{R}^n \rightarrow
2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}
\end{definition}

\subsection{Our contribution}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
  \epsilon$)-equilibria for sequential two-person zero-sum games with
  imcomplete information and perfect recall.

@@

\section{The proposed algorithm}
\label{sec:algo}
\subsection{Algorithm and convergence rate}
We now derive the algorithm derive the algorithm which is the main object of
this manuscript.
